IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/abstract.tex
improve abstract

\begin{abstract}
    Many important security problems in JavaScript, such as browser extension
    security, untrusted JavaScript libraries and
    safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
    of information flow control.
We formally specify a coarse-grained dynamic IFC system that
can be implemented non-intrusively, resulting in
much greater implementation efficiency than previous finer-grained approaches.
The central idea is that an IFC system should model
a set of communicating isolated language runtimes.
The result is a general method for adding IFC to existing
languages that is largely indifferent to the choice of language.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
of information flow control.
We formally define a system in which a coarse-grained dynamic IFC system
can be designed once and then applied to any programming language
for which external effects can be controlled.  We use
this formalism to implement two IFC systems for JavaScript, and show how
it applies to other languages such as C.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}
